---
title: "Urban forest classification and individual crown parameterization"
author: "markusmnzngr"
---


Ready-to-use workflow for urban forest classification and individual crown parameterization based on LiDAR point clouds with a density of at least 4 pts/m².
Initially, the urban forest is classified in the point cloud, followed by the segmentation of individual trees and the derivation of parameters for tree crown reconstruction using geometric primitives. 
Processing of 3D point clouds is memory-intensive, therefore larger areas should be processed in separate tiles. 


## Setup workflow requirements

### Check packages

Check if required packages are installed, otherwise install them.
The workflow is mainly based on the packages *lidR* for point cloud processing and *terra* for spatial data manipulations.
Some functions are also provided by the packages *imager*, *EBImage*, *ForestTools*, *rLiDAR* and *raster*.

```{r check packages}
if (!requireNamespace("lidR", quietly = TRUE))
  install.packages("lidR")
if (!requireNamespace("data.table", quietly = TRUE))
  install.packages("data.table")
if (!requireNamespace("imager", quietly = TRUE))
  install.packages("imager")
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
if (!require("EBImage", quietly = TRUE))
    BiocManager::install("EBImage")
if (!requireNamespace("terra", quietly = TRUE))
  install.packages("terra")
if (!requireNamespace("ForestTools", quietly = TRUE))
  install.packages("ForestTools")
if (!requireNamespace("rLiDAR", quietly = TRUE))
  install.packages("rLiDAR")
if (!requireNamespace("raster", quietly = TRUE))
  install.packages("raster")
if (!requireNamespace("here", quietly = TRUE))
  install.packages("here")
if (!requireNamespace("future", quietly = TRUE))
  install.packages("future")
```


### Define input data paths
The repository contains example data for a small test area in Berlin (Germany) with a tile size of 200 m x 200 m. 
```{r input paths}
raw_lidar_path <- here::here("data/raw", "lidar_point_cloud_berlin_test_area.las")
ndvi_tif_path <- here::here("data/processed","truedop20ndvi_berlin_test_area.tif")
lod2_roof_heights_xyz_path <- here::here("data/processed","lod2_roof_heights_berlin_test_area.csv")
```


### Set workflow variables
variables may vary according to input LiDAR data specifications or available multispectral image

```{r workflow variables}
#### input data ####
# coordinate reference system
tile_crs <- "epsg:25833"

# cell size (m) for point cloud rasterization
cell_size <- 0.5

# LiDAR maximum number of returns
max_nor <- 7

#### roof point classification ####
# buffer roof point classification via LoD2 roof heights
delta_roofheight <- 1.5

# parameters for coplanar point detection
k_cop <-8
th1_cop <- 25
th2_cop <- 6

#### urban forest classification ####
# tree height range (m)
max_h_trees <- 40
min_h_trees <- 2

# watershed segmentation thresholds
ws_th_tree <- 2
ws_tol <- 0.3
ws_ext <- 1

# threshold urban tree mask classification
threshold_combined_metrics <- 0.55

#### individual tree detection
# sigma for Gaussian filtering
sigma_chm <- 0.3

# variable window function for mixed forests from Popescu & Wynne (2004) - https://doi.org/10.14358/PERS.70.5.589
vwf_fun <- function(x){2.51503 + 0.00901 * x^2}
```


### Source custom functions
The repository contains custom functions for specific tasks. 
```{r source functions}
source(here::here("src/R/functions","buffer_gridded_roof_surfaces.R"))
source(here::here("src/R/functions","clean_polygon_parts.R"))
source(here::here("src/R/functions","classify_coplanar_regions.R"))
source(here::here("src/R/functions","calculate_zonal_stats.R"))
source(here::here("src/R/functions","tree_crown_metrics.R"))
source(here::here("src/R/functions","compute_crown_orientation.R"))
source(here::here("src/R/functions","determine_tree_model_prototype.R"))

```

## Data pre-processing 

Read all surface points into a LAS object. It is assumed that that ground points are pre-classified and have the class code 2. If not, they can be classified using ``` lidR::classify_ground() ```.
In the test data provided, outliers are assigned to class 7 and filtered as well.

Tile extent is derived from the point cloud and used to define an empty raster template for point cloud and vector rasterizations.

During the workflow the mean number of returns as well as the Digital Terrain Model (DTM) are needed. Both are derived from the point cloud. 
The DTM is calculated interpolating all ground points to a raster surface. 
The NDVI as a spectral metric indicates vegetation cover.

```{r data pre-processing}
# import all surface points from point cloud
lidar_surface_points <- lidR::readLAS(raw_lidar_path, filter = "-drop_class 2 7")
terra::crs(lidar_surface_points) <- tile_crs

# derive tile extent
tile_ext <- terra::ext(lidar_surface_points)
tile_id <- paste0(terra::xmin(tile_ext), "_", terra::ymin(tile_ext))

# define template 
template <- terra::rast(extent = tile_ext, crs = tile_crs, resolution = cell_size)

# calculate mean number of returns for grid template
mean_nor_grid <- lidR::template_metrics(lidar_surface_points, mean(NumberOfReturns), template)

# import all ground points from point cloud (LAS classification code 2)
lidar_ground_points <- lidR::readLAS(raw_lidar_path, filter =  "-keep_class 2")
terra::crs(lidar_ground_points) <- tile_crs

# calculate DTM using Delaunay triangulation for spatial interpolation
dtm_grid <- lidR::rasterize_terrain(lidar_ground_points, resolution = cell_size, algorithm =  lidR::tin())
# replace NA values with 0
dtm_grid <- terra::ifel(is.na(dtm_grid), 0, dtm_grid)

# read NDVI raster 
ndvi_grid <- terra::rast(ndvi_tif_path)

# remove 
rm(lidar_ground_points)
gc(verbose = FALSE)
```

## Classification of the urban forest
The classification of the urban forest is done in two steps. 
First, buildings as the predominant element in the urban space are filtered from the urban point cloud. 
Subsequently, an urban tree mask is classified by fusing the point cloud with aerial imagery in an object-based image analysis approach 

### Roof point filtering 
If available, existing 3D building models with standardized roofs are used to classify roof points. Therefore the rasterized roof heights are buffered to account for roof overhangs and merged with the point cloud. All points that are less than the specified delta (here 1.5 m) above a roof are filtered.

```{r merge roof heights}
# import LoD2 roof heights xyz file and convert to raster
lod2_roofs_grid <- terra::rast(read.table(lod2_roof_heights_xyz_path, header = TRUE), type = "xyz", crs = tile_crs)

# buffer roofs with custom function to account for roof overhangs
lod2_roofs_grid <- buffer_roof_surfaces(lod2_roofs_grid)

# join buffered roof heights to point cloud 
lidar_surface_points <- lidR::merge_spatial(lidar_surface_points, lod2_roofs_grid, "RoofHeight")

# Assign the user-defined class 30 to points identified as a roof via LoD2 roof height
# delta_roofheight to compensate model inaccuracies
lidar_surface_points@data[(Z-RoofHeight) <= delta_roofheight & RoofHeight > 0, Classification := 30L]

# delete intermediate data
rm(lod2_roofs_grid)
gc(verbose = FALSE)
```


Furthermore, rooftops may also be detected as planar shapes in the point cloud. Thereby they differ well from non-planar objects like trees.

```{r coplanar points classification}
# classify coplanar points as potential roof points
lidar_surface_points <- lidR::segment_shapes(lidar_surface_points, lidR::shp_plane(th1 = th1_cop, th2 = th2_cop,k = k_cop), "Coplanar")

# assign the user-defined class 31 to coplanar points if they have not already been classified as roof
lidar_surface_points@data[Coplanar == TRUE & Classification != 30L, Classification := 31L]

# call custom function to build coplanar regions and to detect all points below z_max of such a region 
lidar_surface_points <- classify_coplanar_regions(lidar_surface_points)

# filter all detected roof points from point cloud
lidar_surface_points <- lidR::filter_poi(lidar_surface_points, Classification != 30L, Classification != 31L & Classification !=32L)
```

### Classification of the urban tree mask ### 

For data fusion the filtered point cloud is rasterized to a normalized Digital Surface Model (nDSM). Watershed Segmentation on the nDSM is used to build segments which approximate tree crown shapes. 
Classification of the individual segments is based on 3 metrics:
* Mean Number of Returns
* Mean NDVI
* Segment compactness

```{r nDSM interpolation}
# height normalize the point cloud with the calculated DTM
lidar_surface_points <- lidR::normalize_height(lidar_surface_points, dtm_grid)

# reclassify negative z-values to 0
lidar_surface_points@data[Z < 0, Z := 0]

# subset points that are higher than user-defined max height for trees
lidar_surface_points <- lidR::filter_poi(lidar_surface_points, Z <= max_h_trees)

# compute nDSM from filtered point cloud 
# usage of point2raster algorithm with subcircle option to densify the point cloud with approximate LiDAR footprint diameter
ndsm_grid <- lidR::rasterize_canopy(lidar_surface_points, res = cell_size, algorithm = lidR::p2r(subcircle = 0.3, na.fill = NULL))

# set all raster cells beneath user-defined minimum tree height to NA
ndsm_grid <- terra::ifel(ndsm_grid < min_h_trees, NA, ndsm_grid)
```


Watershed segmentation may result in fragmented and splintered polygons which are cleaned up before classification.
```{r watershed segmentation}
# perform watershed segmentation with defined parameters
ws_segments_grid <- lidR::watershed(ndsm_grid, th_tree = as.numeric(ws_th_tree), tol=as.numeric(ws_tol), ext=as.numeric(ws_ext))()

# convert segments to polygons - results in multipart polygons
ws_segments_poly <- terra::as.polygons(ws_segments_grid, dissolve = TRUE, values = TRUE, na.rm = TRUE)

# assign a unique id for each polygon
ws_segments_poly[, "obj_id_mp"] <-seq.int(nrow(ws_segments_poly))
ws_segments_poly[, "Z"] <- NULL

# conversion to singlepart polygons
ws_segments_poly <- terra::disagg(ws_segments_poly)

# assign a unique id for each polygon
ws_segments_poly[, "obj_id_sp"] <- seq.int(nrow(ws_segments_poly))
# calculate polygon perimeter and area
ws_segments_poly[, "area"] <- terra::expanse(ws_segments_poly, unit = "m", transform = FALSE)
ws_segments_poly[, "perim"] <- terra::perim(ws_segments_poly)

# clean segments using custom function
ws_segments_cleaned <- clean_segmentation_results(ws_segments_poly)

# delete intermediate data
rm(ws_segments_grid, ws_segments_poly)
gc(verbose = FALSE)
```

For classification the metrics are calculated for each segment and combined to a tree criteria. All segments which exceed the defined threshold for this criteria are classified as tree. 
Based on the classified segments the point cloud can be filtered once more and the Canopy Height Model (CHM) can be extracted from the nDSM. 

```{r tree mask classification}
# calculate mean NDVI for segments with custom function
zonal_ndvi_df <- zonal_stats_as_df(ws_segments_cleaned, "obj_id_aggr", ndvi_grid, "mean_ndvi", "mean")

# calculate mean number of returns for segments with custom function
zonal_mean_nor_df <- zonal_stats_as_df(ws_segments_cleaned, "obj_id_aggr", mean_nor_grid, "mean_nor", "mean")
# scale values to range 0 to 1
zonal_mean_nor_df[, "zonal_mean_nor_weighted"] <- with(zonal_mean_nor_df, mean_nor/max_nor)

# calculate Isoperimetric Quotient (IPQ) as shape metric and weight with shape area
# retrieve segment area and perimeter from attribute table
ws_segments_ipq_df <- terra::as.data.frame(ws_segments_cleaned)
# calculate IPQ
ws_segments_ipq_df[, "ipq"] <- with(ws_segments_ipq_df,(4*pi*area)/(perim*perim))
# weight IPQ based on shape area, smallest area is one cell
ws_segments_ipq_df[, "area_weighted"] <- with(ws_segments_ipq_df,ifelse(area < 30, round((area - (cell_size*cell_size))/(30 - (cell_size*cell_size)), digits = 2), 1))
ws_segments_ipq_df[, "ipq_area_weighted"] <- with(ws_segments_ipq_df,ipq * area_weighted)
# clean data.frame columns
ws_segments_ipq_df <- ws_segments_ipq_df[c("obj_id_aggr", "ipq", "area_weighted", "ipq_area_weighted")]

# combine the metric tables
criteria_join_df <- merge(ws_segments_ipq_df, merge(zonal_ndvi_df, zonal_mean_nor_df, by = "obj_id_aggr", all.x = TRUE), by = "obj_id_aggr", all.x = TRUE)
# combine the metrics to one tree criteria
criteria_join_df[, "tree_criteria"] <- with(criteria_join_df, zonal_mean_nor_weighted + ipq_area_weighted + mean_ndvi)

# join metrics to segments
ws_segments_cleaned <- terra::merge(ws_segments_cleaned, criteria_join_df, by = "obj_id_aggr")

# classify segments through subset
ws_segments_cleaned <- terra::subset(ws_segments_cleaned,  ws_segments_cleaned$tree_criteria >= threshold_combined_metrics)

# Extract CHM with classified tree segments
ndsm_grid <- terra::mask(ndsm_grid, ws_segments_cleaned, inverse=FALSE, updatevalue=NA, touches=FALSE)

# store as raster GeoTIFF
ndsm_grid_out_path <- here::here("results/urban_forest_classification", "chm_grid.tif")
terra::writeRaster(ndsm_grid, ndsm_grid_out_path, overwrite = TRUE)

# merge CHM to point cloud - identify points intersecting the CHM
lidar_surface_points <- lidR::merge_spatial(lidar_surface_points, ndsm_grid, attribute = "CHM")

# filter point cloud - keep only points intersecting the CHM  
lidar_surface_points <- lidR::filter_poi(lidar_surface_points, !is.na(CHM))

# remove duplicate points based on their XYZ-coordinates
lidar_surface_points <- lidR::filter_duplicates(lidar_surface_points)

# store LiDAR point cloud as LAS
lidar_chm_points_out_path <- here::here("results/urban_forest_classification", "lidar_chm_points.las")
lidR::writeLAS(lidar_surface_points, lidar_chm_points_out_path)

# delete intermediate data
rm(zonal_ndvi_df, zonal_mean_nor_df, ws_segments_ipq_df, criteria_join_df, ws_segments_cleaned)
gc(verbose = FALSE)

```


## Individual crown segmentation 

Individual trees are detected by filtering local maxima (LM) on the Gaussian smoothed CHM as treetops. 
Starting from the treetops, tree crowns are derived with marker-controlled watershed segmentation (MCWS).
MCWS may result in fragmented and splintered polygons which are cleaned up before further processing.
```{r crown segmentation}
# define focal weight matrix with Gaussian filter
gf <- terra::focalMat(ndsm_grid, sigma_chm, 'Gauss')
# smooth CHM with focal matix - no na.rm to "thin out" tree segments
ndsm_gaussian_grid <- terra::focal(ndsm_grid, w=gf)

# filter for local maxima with variable window of circular shape
# convert results from sf to SpatVector
ttops_vwf <- terra::vect(lidR::locate_trees(ndsm_gaussian_grid, lidR::lmf(vwf_fun, hmin = 2, shape = "circular")))

# use MCWS function from package ForestTools
# convert tree tops to SpatialPointsDataFrame
# https://stackoverflow.com/questions/64035643/converting-spatvector-to-sf-or-sp
ttops_vwf <- sf::as_Spatial(sf::st_as_sf(ttops_vwf))
# segment crowns with mcws
mcws_segments_grid = terra::rast(ForestTools::mcws(ttops_vwf, raster::raster(ndsm_grid), minHeight = 2, format = "raster"))

# Convert crown segments to polygon - results in multipart polygons
mcws_segments_poly <- terra::as.polygons(mcws_segments_grid, dissolve = TRUE, values = TRUE, na.rm = TRUE)

# assign a unique id for each polygon
mcws_segments_poly[, "obj_id_mp"] <- seq.int(nrow(mcws_segments_poly))
mcws_segments_poly[, "Z"]<- NULL


#### clean MCWS segments ####
# conversion to singlepart polygons
mcws_segments_poly <- terra::disagg(mcws_segments_poly)

# assign a unique id for each polygon
mcws_segments_poly[, "obj_id_sp"] <- seq.int(nrow(mcws_segments_poly))
# calculate perimeter and area
mcws_segments_poly[, "area"] <- terra::expanse(mcws_segments_poly, unit = "m", transform = FALSE)
mcws_segments_poly[, "perim"] <- terra::perim(mcws_segments_poly)

# clean segments using custom function
crowns_mcws_poly <- clean_segmentation_results(mcws_segments_poly)

# convert to raster 
crowns_mcws_grid <- terra::rasterize(crowns_mcws_poly, template, field = "obj_id_aggr", background = NA, touches = FALSE, update = TRUE)

# delete intermediate data
rm(gf, ndsm_gaussian_grid, vwf_fun, ttops_vwf,mcws_segments_grid, mcws_segments_poly)
gc()
```



## Tree crown parameterization
Geometric tree crown parameters are derived from the 3D point cloud. Therefore the point cloud is filtered and segemnted according to the MCWS segments. Crown extents are approximated 
by the 2D convex hull around tree points. 3D convex hulls are calculated to retrieve volume and surface area of the crowns. 

```{r tree crown parameterization}
# segment point cloud according to MCWS segments
lidar_surface_points <- lidR::merge_spatial(lidar_surface_points, crowns_mcws_grid, "treeID_temp")

# count pulses per crown and crown dimensions
pulse_count <- lidar_surface_points@data[, .(count=.N, delta_x = max(X) - min(X), delta_y = max(Y) - min(Y), delta_z = max(Z) - min(Z)), by = "treeID_temp"]
  
# join pulse count to lidar data
lidar_surface_points@data <- merge(lidar_surface_points@data, pulse_count, by = "treeID_temp")

 # subset crowns with less than 4 points or are not shaped in all 3 dimensions to avoid mistakes in metric calculations and points that don't belong to a tree crown 
  lidar_surface_points <- lidR::filter_poi(lidar_surface_points, !is.na(treeID_temp) & count > 4 & delta_x > 0.1 & delta_y > 0.1 & delta_z > 0.1)

# calculate 3D convex hulls around segmented tree points
# retrieve volume and surface area of the hulls
crown_volumes_df <- compute_crown_volumes(lidar_surface_points, "treeID_temp")

# join volumes to point cloud
lidar_surface_points@data <- merge(lidar_surface_points@data, crown_volumes_df, by = "treeID_temp")
  
# filter "trees" without volume to avoid errors in polygon construction
lidar_surface_points <- lidR::filter_poi(lidar_surface_points, crownvolume > 0)

# join NDVI grid to point cloud
lidar_surface_points <- lidR::merge_spatial(lidar_surface_points, ndvi_grid, "ndvi")
  
# assign variable names for 2D crown metrics function 
ccm = ~calculate_crown_metrics(z = Z, nor = NumberOfReturns, ndvi = ndvi)

# compute 2D convex hull for each tree crown and calculate 2D crown metrics
crowns_convex_hull_poly <- terra::vect(lidR::crown_metrics(lidar_surface_points, func = ccm, geom = "convex", attribute = "treeID_temp"))

# calculate area of convex hulls
crowns_convex_hull_poly[, "ch_area"] <- terra::expanse(crowns_convex_hull_poly, unit = "m", transform = FALSE)

# join 3D crown volumes to 2D convex hulls
crowns_convex_hull_poly <- terra::merge(crowns_convex_hull_poly, crown_volumes_df, by = "treeID_temp")

# filter tree crowns that are to small to build volume or where neither NDVI or Mean Number of Returns are above thresholds
crowns_convex_hull_poly <- terra::subset(crowns_convex_hull_poly,(crowns_convex_hull_poly$mean_ndvi > 0.1 | crowns_convex_hull_poly$mean_nor  >= 2) & crowns_convex_hull_poly$crownvolume != 0)

# create final sequential treeID
crowns_convex_hull_poly[, "treeID"] <- seq.int(nrow(crowns_convex_hull_poly))

# create column treeID based on tile extent
crowns_convex_hull_poly[, "treeID_tile"] <- paste0('tile_', tile_id, '_tree_', crowns_convex_hull_poly$treeID)

```


## Tree crown reconstruction and prototype assignment 
Individually scaled prototypes enable efficient modeling for numerous tree objects. 
This repository contains 10 prototypes composed of geometric primitives. Tree crowns are approximated with ellipsoids and trunks with cylinders. The 10 pre-defined prototypes differ in their ratio of crown height to trunk height. Depending on the identified parameters, a prototype is assigned to each tree.
To individually scale and rotate the prototypes, the crown extent is approximated by an ellipse fitted to the 2D convex hull. 
Height parameters have been derived in the previous step. 
Finally the parameterized tree positions and convex hulls are output.


```{r tree crown reconstruction}
# calculate shortest distance between two vertices of the convex hulls as data.frame
ch_width_df <- as.data.frame(terra::width(crowns_convex_hull_poly, as.lines = FALSE))
# rename data.frame column 
names(ch_width_df)[1] <- "ch_width"
# add column treeID 
ch_width_df[, "treeID"] <- seq.int(nrow(ch_width_df))
# join to features 
crowns_convex_hull_poly <- terra::merge(crowns_convex_hull_poly, ch_width_df, by = "treeID")

# call custom function to compute antipodal pair as longest distance between two vertices and get orientation of the line connecting the antipodal pair
crown_orientation_df <- compute_crown_orientation(crowns_convex_hull_poly)
# join to features 
crowns_convex_hull_poly <- terra::merge(crowns_convex_hull_poly, crown_orientation_df, by = "treeID")

# derive tree trunk position as centroid of the convex hull
tree_positions_point <- terra::centroids(crowns_convex_hull_poly)

# calculate x and y of tree position as data.frame
tree_positions_xy_df <- terra::crds(tree_positions_point, df = TRUE)
# add column treeID 
tree_positions_xy_df[, "treeID"] <-  seq.int(nrow(tree_positions_xy_df))
#rename data.frame columns
names(tree_positions_xy_df) <- c("X", "Y", "treeID")

# calculate Z as tree base height from DTM
# use custom zonal statistics function to derive Z-Value for each position
tree_positions_z_df <- zonal_stats_as_df(tree_positions_point, "treeID", dtm_grid, "Z", "max") 

# combine xy and z data.frames
tree_positions_xyz_df <- merge(tree_positions_xy_df, tree_positions_z_df, by = "treeID")

# join to tree positions
tree_positions_point <- terra::merge(tree_positions_point, tree_positions_xyz_df, by = "treeID")

# get all attributes as data.frame
tree_attribs_df <- terra::values(tree_positions_point)

# calculate crown metrics 
tree_attribs_df[, "h_tree"] <- tree_attribs_df[, "z_max"]
tree_attribs_df[, "h_crown"] <- tree_attribs_df$z_max - tree_attribs_df$zq5
tree_attribs_df[, "d_crown"] <- (tree_attribs_df$ch_width + tree_attribs_df$ch_length)/2
tree_attribs_df[, "h_trunk"] <- tree_attribs_df[, "zq5"]

# call custom function to define modeling prototype based on ratio of crown height to trunk height
thresholds <- define_prototype_thresholds(count_prototypes = 10)

# call custom function to assign a prototype
tree_attribs_df[, "tree_model"] <- assign_tree_model_ifelse(h_trunk = tree_attribs_df$h_trunk, h_crown = tree_attribs_df$h_crown, thresholds = thresholds)

# list all numeric columns
num_cols <- vapply(tree_attribs_df, is.numeric, FUN.VALUE = logical(1))
# round all numeric columns to two digits
tree_attribs_df[,num_cols] <- round(tree_attribs_df[,num_cols], digits = 2)

# reorder columns
tree_attribs_df <- tree_attribs_df[, c("treeID", "treeID_tile", "h_tree", "h_crown", "d_crown", "h_trunk", "X", "Y", "Z",
  "ch_width", "ch_length", "ch_orientation", "ch_area",
  "tree_model", "crownvolume", "crownsurface", "n_pulses", "mean_nor", "mean_ndvi",
  "z_max", "z_min", "z_mean", "z_std", "zq1", "zq2", "zq5", "zq95", "zq99")]

# delete the temporary attribute tables 
tree_positions_point <- tree_positions_point[,"treeID"]
crowns_convex_hull_poly <- crowns_convex_hull_poly[, "treeID"]

# join final attribute table to the geometries
tree_positions_point <- terra::merge(tree_positions_point, tree_attribs_df, by = "treeID")
crowns_convex_hull_poly <- terra::merge(crowns_convex_hull_poly, tree_attribs_df, by = "treeID")

# store tree positions as geojson
tree_positions_out_path <-  here::here("results/parameterized_tree_crowns", "tree_positions_parameterized.geojson")
terra::writeVector(tree_positions_point, tree_positions_out_path, filetype = "GeoJSON", overwrite = TRUE)

# store tree crowns as geojson
crowns_convex_hull_parameterized_out_path <-  here::here("results/parameterized_tree_crowns", "crowns_convex_hull_parameterized.geojson")
terra::writeVector(crowns_convex_hull_poly, crowns_convex_hull_parameterized_out_path, filetype = "GeoJSON", overwrite = TRUE)
```







